Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-09 manuscript/manuscript.tex
addressed comments

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}
\allowdisplaybreaks

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it is invariant to monotone marginal
transformations. To generate the samples to which our
method would be applied, we simulated a time series $W_t$ from a 1st 
order autoregressive or AR(1) process:
\begin{equation*}
W_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
\jy{What was the value of $\sigma_\epsilon$?}
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: 
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_t$ by
\begin{equation*}
X_t = F^{-1}[\Phi(W_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution.
After the transformation
to the marginal gamma distribution, the lag-1 autocorrelations are
\[
  \{-0.884, -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}.
\]

@@

\input{tables/rr_norm}

\input{tables/rr_gamma}

\jy{merge the two tables; use bottomrule and toprule instead of hline;
  put them in this file instead of inputing.}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{Power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and marginal distribution 
    $\in \{N(8,8), \Gamma(8,1)\}$.\jy{clarify the data generating distribution and the
      hypothesized distribution}
  }
  \label{fig:rr}
\end{figure}

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
found that our method doesn't work under the null hypothesis for such high
dependence levels. It appears that rejection rate seems to decline as $\tau$
\jy{comment on the asymmetry of the power in response to tau.}
increases. Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in 
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
when a large enough sample size is used.

@@

\jy{QC bib entries: page numbers missing for some journal articles.}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{multirow}
\allowdisplaybreaks

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence as it is invariant to monotone marginal
transformations. To generate the samples to which our
method would be applied, we simulated a time series $W_t$ from a 1st 
order autoregressive or AR(1) process:
\begin{equation*}
W_t = \phi W_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
\jy{What was the value of $\sigma_\epsilon$?}\mc{addressed}
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: 
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. The 
series $W_t$ has mean zero and variance 
$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
$\phi$, 
we 
set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_t$ by
\begin{equation*}
X_t = F^{-1}[\Phi(W_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution.
After the transformation
to the marginal gamma distribution, the lag-1 autocorrelations are
\[
  \{-0.884, -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}.
\]

@@

\jy{merge the two tables; use bottomrule and toprule instead of hline;
  put them in this file instead of inputing.}\mc{addressed, let me know if I 
  should combine them in a different way}

\begin{table}[ht]
\centering
\caption{Rejection rates for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels.} 
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.052 & 0.013
& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& \multirow{3}{2em}{200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& \multirow{3}{2em}{400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& \multirow{3}{2em}{800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ 
\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\ 
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & \multirow{3}{2em}{200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & \multirow{3}{2em}{400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & \multirow{3}{2em}{800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule

\end{tabular}
\end{table}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{Power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution 
    $\in \{N(8,8), \Gamma(8,1)\}$. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from 
    $\Gamma(8,1)$, we tested for the normal family. \jy{clarify the data generating distribution and the
      hypothesized distribution}\mc{addressed}
  }
  \label{fig:rr}
\end{figure}

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
found that our method doesn't work under the null hypothesis for such high
dependence levels. It appears that rejection rate seems to decline as $\tau$
\jy{comment on the asymmetry of the power in response to tau.}\mc{addressed}
increases. Rejection rates are negatively affected by positive serial 
dependence, but they do not seem to be affected by negative serial dependences
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in 
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
when a large enough sample size is used.

@@

\jy{QC bib entries: page numbers missing for some journal articles.}
\mc{couldn't find it for naess2012application}
